Energy-Aware Planning-Scheduling for\\Autonomous Aerial Robots

### 2022-05-21 review/response-letter.tex

{\hspace*{-4.5em}{[R1:7]}\vspace*{-1.9em}}

Thank you for underlying the issue regarding the definition of stage. We are using the indices $j$ and $k$ to indicate that there might be a different constraint per each parameter and the numbers of parameters $\rho$ and $\sigma$ to indicate that there might be a different number of parameters. Nonetheless, we acknowledge the necessity to exemplify these in a better manner.

We have updated the definition for this purpose.

\begin{formal}
  \color{black} 
  \textbf{Definition}~II.1~(Stage)\textbf{.}~[...] the $i$th \emph{stage} $\Gamma_i$ %at time instant $t$ %of a plan $\Gamma$ 
    is
  \begin{equation*}\begin{split}
      \Gamma_i:=\{{\color{blue}\varphi_i(\mathbf{p}%(t)
      ,c_i^\rho)},c_i^\sigma\mid
      \,&\forall j\in\,[\rho]_{>0},\,c_{i,j}\,\,\,\,\,\,\,\in\mathcal{C}_{i,j},\,\\
        &\forall k\in[\sigma]_{>0},\,c_{i,\rho+k}\in\mathcal{S}_{i,k}\,\},
  \end{split}\end{equation*}
  where $c_i^\rho${\color{blue}$:=\{c_{i,1},c_{i,2},\dots,c_{i,\rho}\}$} and $c_i^\sigma${\color{blue}$:=\{c_{i,\rho+1},c_{i,\rho+2},\dots,$ $c_{i,\rho+\sigma}\}$} are $\rho$ \emph{path} and $\sigma$ \emph{computation parameters}{\color{blue}, e.g., $c_i^\rho:=\{c_{i,1}\}$ is a value that changes the distance of the coverage lines and $c^\sigma_i:=\{c_{i,2}\}$ the detection rate with $\rho$ and $\sigma$ being one (see Section~{\color{red}V})}. $\mathcal{C}_{i,j}:=[\underline{c}_{i,j},\overline{c}_{i,j}]\subseteq\mathbb{R}$ is the $j$th path parameter %$c_{i,j}$ 
  constraint set, %and 
  $\mathcal{S}_{i,k}:=[\underline{c}_{i,\rho+k},\overline{c}_{i,\rho+k}]\subseteq\mathbb{Z}_{\geq 0}$ %is 
  the $k$th computation parameter constraint set. {\color{blue}Indices $j,k$ serve~to~differentiate path and computation parameters constraints and indicate that each parameter can have a different constraint set.}
  \vspace*{1ex}
\end{formal}

@@

Thank you for noticing that a citation and clarification are missing regarding the energy models. The items of matrices $A$ and $C$ are constructed so that the two periodic models, the model in Equation ({\color{red}2}) and Equation ({\color{red}3}) match under some conditions (the value of the initial guess is described by Equation ({\color{red}8}) and the model is not perturbed by the control).

$A$ is then a skew-symmetric matrix that contains sub-matrices $A_j$ utilized for the periodic behavior with the frequencies $\omega:=2\pi/T$ ($T$ is the period). Each frequency is multiplied by $j$ from one up to the order $r$, where $j$ is the index of the sub-matrix, i.e., there are $r$ frequencies modeling the periodicity one the base frequency.

We have elaborated further in Section III-A to reflect the observation and added a reference to the corresponding author's Ph.D. thesis (reference [{\color{green}31}], Section 4.3.1).

\begin{formal}
  {\color{black}
  [...] {\color{blue}Matrices $A$ and $C$ are constructed such that t}he %Under favorable conditions, %the 
  models in Eqs.~({\color{red}2}--{\color{red}3}) {\color{black}are equal when $\mathbf{u}$ is a {\color{black}zero vector %, matrices $A,C$ described by Eqs.~(\ref{eq:mat_A}--\ref{eq:mat_C}), 
  and an initial guess $\mathbf{q}(t_0)=\mathbf{q}_0$ at {\color{blue}the} initial time instant $t_0$}}
    {\color{blue}\begin{equation}\tag{8}
    {\color{black}\mathbf{q}_0=\begin{bmatrix}a_0 & a_1/2 & b_1/2 & \cdots & a_r/2 & b_r/2\end{bmatrix}',}
    \end{equation}}
    %$h$ in Eq.~(\ref{eq:fourier}) is equal to $y$ in Eq.~(\ref{eq:state-perf}).
  %\end{lem}
  %\begin{proof}
  %The equality of the signal and output is achieved by a proper choice of the items of matrices $A,C$ and the initial guess $\mathbf{q}_0$. We refer the reader to Appendix~\ref{app:proof-eqv} for a formal proof, where we justify the choices of the items of the matrices and of the initial guess. 
  %\end{proof}
  %Appendix~\ref{app:proof-eqv} contains a proof of Lem.~\ref{lem:eqv}.
  \color{black}i.e., $h,y$ are both harmonic signals with the same frequencies. {\color{blue}Further details see the first author's Ph.D. thesis~[{\color{green}31}]}.
  }
  \vspace*{1ex}
\end{formal}
}

@@

{\color{blue}

{\hspace*{-4.5em}{[R2:8]}\vspace*{-1.9em}}

Thank you for spotting the issue in the introductory section. We have corrected the sentence.

\begin{formal}
  \color{black} [...] Such use cases arise in precision agriculture~[{\color{green}4}] where {\color{blue}information collection prior to a harvesting operation and} damage prevention during the operation involve aerial robots~[{\color{green}5}],~[{\color{green}6}].

### 2022-05-21 energy-planning.tex
proofreading

\vspace*{-2.6ex}
%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}  %
\label{sec:intro}       %
                        %
\IEEEPARstart{U}{se cases} involving aerial robots span broadly. They comprise diverse planning and scheduling strategies and often require high autonomy under strict energy budgets. 
One such use case is coverage path planning (CPP)~\cite{choset2001coverage,galceran2013survey}, which consists of, e.g., an aerial robot visiting every point in a given space~\cite{cabreira2019survey} while running assigned computational tasks. Here, the aerial robot might detect ground patterns and notify other ground-based actors. %with little human interaction. 
Such use cases arise in %, e.g., 
precision agriculture~\cite{hajjaj2014review} 
where 
{\color{blue}information collection prior to an harvesting operation and}
%harvesting involves ground vehicles~\cite{%qingchun2012study,
%dong2011development, de2011design%,aljanobi2010setup, 
%li2008analysis, 
%edan2000robotic
%}, information collection prior to an operation as well as 
damage prevention during the operation involve aerial robots~\cite{puri2017agriculture, daponte2019review}.
Microcontrollers and heterogeneous computing hardware~\cite{mei2005case} (i.e., with CPUs and GPUs) running power-demanding computational tasks are frequently mounted onto the robots in these and many other scenarios~\cite{william2019aerial%, peng2019evaluating,
%wang2020yolo
,alexey2021autonomous}.
%In these and many others, the robot frequently mounts microcontroller and heterogeneous computing hardware~\cite{mei2005case} (i.e., with CPUs and GPUs) running power-demanding computational tasks~\cite{william2019aerial, peng2019evaluating,wang2020yolo,alexey2021autonomous}. 
We refer to onboard computational tasks that can be scheduled with an energy impact as \emph{computations}. We are interested in the energy optimization of motion plans and computations schedules in-flight and refer to it as energy-aware \emph{planning-scheduling}. 
The energy optimization of computations schedules can be achieved by, e.g., varying the quality of service between specific bounds~\cite{ho2019qos} and frequency and voltage of the computing hardware~\cite{mei2005case,brateman2006energy,zhang2007low}. We focus on the former aspect and schedule the onboard computations altering their quality while simultaneously changing the quality of the coverage.
{\color{blue} Concretely, we alter how often the aerial robot detects ground patterns along with the distance of the lines that form the coverage.}
Fig.~\ref{fig:il-abs} illustrates the intuition: an aerial robot flies a plan with maximal coverage and schedule~(\ref{sth:i}), that is optimized during flight to respect the battery state~(\ref{sth:ii}), and altered due to, e.g., unexpected battery defects~(\ref{sth:iii}).

@@

There are numerous planning approaches applied to a variety of robots. An instance is an algorithm selecting an energy-optimized trajectory~\cite{mei2004energy} by, e.g., maximizing the operational time~\cite{wahab2015energy}. Many approaches apply to a small number of robots~\cite{kim2005energy} and focus exclusively on planning the trajectory~\cite{kim2008minimum}, despite compelling evidence of the energy influence of onboard consumptions~\cite{mei2005case,ondruska2015scheduled,sudhakar2020balancing,brateman2006energy}. In view of the availability of powerful heterogeneous computing hardware~\cite{rizvi2017general}, the use of onboard computations is further expected to increase in the foreseeable future~\cite{%abramov2012real,
%satria2016real,
jaramillo2019visual}. In this context, planning-scheduling energy awareness is a recent research direction% energy awareness for mobile robots are scarce
~\cite{brateman2006energy,sudhakar2020balancing,lahijanian2018resource,ondruska2015scheduled}. Early studies (2000--2010) varied hardware-dependent aspects, e.g., frequency, voltage, along with motion aspects, e.g., motor and travel velocities~\cite{mei2005case,brateman2006energy,zhang2007low,sadrpour2013mission} whereas the literature from the past decade derives energy-aware plans-schedules in broader terms. These include simultaneous considerations for planning-scheduling in perception~\cite{ondruska2015scheduled}, localization~\cite{lahijanian2018resource}, navigation~\cite{ho2019qos}, and anytime planning~\cite{sudhakar2020balancing}.
These studies are focused on ground-based robots~\cite{mei2005case,sadrpour2013mission,lahijanian2018resource,ondruska2015scheduled}, yet, aerial robots are particularly affected by energy considerations, as it would be generally required to land to recharge the battery. 
{\color{blue}In terms of aerial coverage, past work considers criteria including the completeness of the coverage and resolution~\cite{difranco2015energy}, and deals with aspects such as the quality of the cover~\cite{difranco2016coverage}, but neglects the energy expenditure of computations and favors rotary-wing aerial robots rather than aerial robots broadly.} 
Such a state of practice has prompted us to propose the planning-scheduling approach for autonomous aerial robots, combining the past body of knowledge but addressing aerial robots' peculiarities such as the atmospheric, battery, and turning radius constraints. Numerical simulations and experimental data of both static and dynamic plans and schedules show improved power savings and fault tolerance with the %aerial 
robot %s
remedying in-flight failures.

Our focus is on fixed wings, i.e., airborne robots where wings provide lift, propellers provide forward thrust, and control surfaces perform maneuvering. Here, motion and computations energies are within an order of magnitude from each other~\cite{seewald2020mechanical}. %Indeed 
{\color{blue}T}here are other classes where planning-scheduling energy awareness leads to irrelevant savings, i.e., when the motion energy contribution far outreaches the computations or vice-versa. The {\color{blue}motion outreaching computation energy} frequently happens with rotary-wing aerial robots (e.g., quadrotors or quadcopters, hexacopters, etc.){\color{blue}, the opposite occurs with} lighter-than-air aerial robots (e.g., blimps). It is a common theme with wider planning-scheduling literature, focusing on energy-efficient ground-based robots such as Pioneer~3DX~\cite{ho2019qos,mei2005case}, ARC~Q14~\cite{ondruska2015scheduled,lahijanian2018resource}, and Pack-Bot~UGV~\cite{sadrpour2013mission}.
%\begin{ctb}
%  We extend the literature on planning-schedu- ling to CPP with aerial robots, model the overall and computations energies and battery evolution, and derive a variable coverage motion for constrained systems, e.g., fixed wings.
%\end{ctb}

To guarantee energy awareness, our approach uses optimal control {\color{blue} and heuristics} where both the paths and schedules variations are trajectories, varying between given bounds (i.e., physical constraints of the robot and computing hardware, quality of service, desired quality of the coverage, etc.). Past planning-scheduling studies also employ optimization techniques~\cite{brateman2006energy,zhang2007low,ondruska2015scheduled,lahijanian2018resource}; some use a greedy approach~\cite{mei2005case,sudhakar2020balancing,sadrpour2013mission}; whereas others use reinforcement learning-based approaches~\cite{ho2019qos,ho2018towards}. {\color{blue}Hybrid approaches~\cite{ondruska2015scheduled} are also available, where the techniques are mixed.} Both the path and schedules variations trajectories are derived for future time instants employing computations and overall energies and battery models. The energy model for the computations uses regressional analysis from our earlier study on heterogeneous computing hardware% energy modeling
~\cite{seewald2019coarse,seewald2019component}, whereas the battery uses an equivalent circuit model (ECM) from the literature~\cite{%he2011evaluation,
hinz2019comparison,mousavi2014various}. The overall model wraps these two aspects in a cohesive model that uses dynamics modeling to predict the energy behavior of future plans and schedules. In Fig.~\ref{fig:il-abs}, collected energy data ({\color{blue}top-right}) and spectrum analysis ({\color{blue}below}) of a fixed wing %aerial robot 
flying CPP motivates the overall energy model: the evolution is periodic--CPP often involves repetitive motions to cover the space~\cite{choset2001coverage,galceran2013survey}--an observation exploited in Section~\ref{sec:energy-model}.% for the computations and motion energies and battery models.

@@

\begin{figure}[t]
  \footnotesize
  \begin{minipage}[l]{0.38\columnwidth}
    \caption{Definitions~\ref{def:stage}--\hyperref[def:plan]{4} on a slice of the plan $\Gamma$. $\mathbf{p}_{\Gamma_i}$ are triggering points in which proximity happens change of stages $\Gamma_i$. Each contains a path function $\varphi_i$ and parameters to alter the path and schedule $c_{i,1},\dots$.}
    \label{fig:traj1}
  \end{minipage}\hfill
  \begin{minipage}[c]{0.6\columnwidth}
    \centering
    \vspace*{-4ex}
    \input{\figpath/new/traj1.tikz}
  \end{minipage}
  \vspace*{-4.5ex}
\end{figure}

@@

\begin{defn}[Stage]\label{def:stage}
  Given a generic point $\mathbf{p}\in\mathbb{R}^2$ w.r.t. a reference frame $\mathcal{O}_W$ of the aerial robot flying at a given altitude $h\in\mathbb{R}_{>0}$, the $i$th \emph{stage} $\Gamma_i$ %at time instant $t$ %of a plan $\Gamma$ 
  is
  \begin{equation*}\begin{split}
    \Gamma_i:=\{{\color{blue}\varphi_i(\mathbf{p}%(t)
    ,c_i^\rho)},c_i^\sigma\mid
    \,&\forall j\in\,[\rho]_{>0},\,c_{i,j}\,\,\,\,\,\,\,\in\mathcal{C}_{i,j},\,\\
      &\forall k\in[\sigma]_{>0},\,c_{i,\rho+k}\in\mathcal{S}_{i,k}\,\},
  \end{split}\end{equation*}
  where $c_i^\rho${\color{blue}$:=\{c_{i,1},c_{i,2},\dots,c_{i,\rho}\}$} and $c_i^\sigma${\color{blue}$:=\{c_{i,\rho+1},c_{i,\rho+2},\dots,$ $c_{i,\rho+\sigma}\}$} are $\rho$ \emph{path} and $\sigma$ \emph{computation parameters}{\color{blue}, e.g., $c_i^\rho:=\{c_{i,1}\}$ is a value that changes the distance of the coverage lines and $c^\sigma_i:=\{c_{i,2}\}$ the detection rate with $\rho$ and $\sigma$ being one (see Section~\ref{sec:experimental})}. $\mathcal{C}_{i,j}:=[\underline{c}_{i,j},\overline{c}_{i,j}]\subseteq\mathbb{R}$ is the $j$th path parameter %$c_{i,j}$ 
  constraint set, %and 
  $\mathcal{S}_{i,k}:=[\underline{c}_{i,\rho+k},\overline{c}_{i,\rho+k}]\subseteq\mathbb{Z}_{\geq 0}$ %is 
  the $k$th computation parameter constraint set. {\color{blue}Indices $j,k$ serves~to~differentiate path and computation parameters constraints and indicate that each parameter can have a different constraint set.} 
\end{defn}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Energy Models}  %
\label{sec:energy-model} %
                         %
The solution to the problem requires energy models, predicting the impact of changes to path and computation parameters on the battery. %at future time instants. To this end, 
Sections~\ref{sec:mod-mot}--\hyperref[sec:mod-bat]{C} provide models for the overall and computations energies {\color{blue}and }%as well as 
battery evolution.

@@

{\color{blue}Matrices $A$ and $C$ are constructed such that t}he %Under favorable conditions, %the 
models in Eqs.~(\ref{eq:fourier}--\ref{eq:state-perf}) are equal
%\begin{lem}[Signal, output equality]\label{lem:eqv}Given 
when $\mathbf{u}$ is a zero vector %, matrices $A,C$ described by Eqs.~(\ref{eq:mat_A}--\ref{eq:mat_C}), 
and an initial guess $\mathbf{q}(t_0)=\mathbf{q}_0$ at initial time instant $t_0$
  {\color{blue}\begin{equation}
  {\color{black}\mathbf{q}_0=\begin{bmatrix}a_0 & a_1/2 & b_1/2 & \cdots & a_r/2 & b_r/2\end{bmatrix}',}
  \end{equation}}
  %$h$ in Eq.~(\ref{eq:fourier}) is equal to $y$ in Eq.~(\ref{eq:state-perf}).
%\end{lem}
%\begin{proof}
%The equality of the signal and output is achieved by a proper choice of the items of matrices $A,C$ and the initial guess $\mathbf{q}_0$. We refer the reader to Appendix~\ref{app:proof-eqv} for a formal proof, where we justify the choices of the items of the matrices and of the initial guess. 
%\end{proof}
%Appendix~\ref{app:proof-eqv} contains a proof of Lem.~\ref{lem:eqv}.
i.e., $h,y$ are %both 
harmonic signals with the same frequencies{\color{blue}. For further details see the first author's Ph.D. thesis~\cite{seewaldphdthesis}}.

@@

Eq.~(\ref{eq:state-perf}) states that the output $y$ evolves in $\mathbb{R}$, %conflicting with the the findings in this section. 
yet, aerial robots usually use a battery.
We thus use instead
%\begin{defn}[Output constraint]\label{def:const}
\begin{equation}\label{eq:output-const}
  {\small\mathcal{Y}(t):=\{y\mid y\in[0,b\,Q_cV]\subseteq{\mathbb{R}_{\geq 0}}\},} 
\end{equation}
%the \emph{output constraint}, 
where $b\,Q_cV$, the maximum instantaneous energy %consumption
measured in watts, is derived from Eq.~(\ref{eq:batdyn}--\ref{eq:batdyn2}).
%\end{defn}

@@

%The algorithm that we presented in this paper is motivated by a periodic behavior of empirical data on energy consumption (see the subfigures of Fig.~\ref{fig:il-abs}). 
Fig.~\ref{fig:il-abs} details the data of the physical flight  
%We collected these data flying Opterra, a fixed-wing UAV that we adapted for an agricultural scenario. The UAV was flying 
in standard atmospheric conditions. 
Fig.~\ref{fig:stat}{\color{blue}--\ref{fig:dyn}} extends the flight with the computing hardware aided by a flight simulation implemented in \textsc{Matlab}\hspace{.5ex}(R). 
Upper-case roman numerals I,II indicate the plans are static (i.e., solely Algorithm~\ref{alg2}), lower-case i,ii exploit planning-scheduling as described in this letter.

@@

Fig.~{\color{blue}\hyperref[fig:stat]{6a}--\hyperref[fig:dyn]{7a}} 
illustrate the same plan $\Gamma$ under different conditions. Flights \hyperref[fig:trajs-I-static]{I}--\hyperref[fig:trajs-dyn-i]{i} have a constant wind speed of five meters per second, a wind direction of zero degrees, and initial parameters $c_{i,1},c_{i,2}$ values of zero and ten (i.e., full $r_2$ and detection). Flights \hyperref[fig:trajs-II-static]{II}--\hyperref[fig:trajs-dyn-ii]{ii} (see added gray background for clarity) are the same but a wind direction of 90 degrees and the initial parameters values of -1000 and two (i.e., minimum $r_2$ and detection). 
{\color{blue} The initial values of path and computation parameters are chosen to represent the highest and lowest configurations in the search space in \hyperref[fig:trajs-I-static]{I}--\hyperref[fig:trajs-dyn-i]{i} and \hyperref[fig:trajs-II-static]{II}--\hyperref[fig:trajs-dyn-ii]{ii} respectively, modeling the behavior of the best- and worst-case scenarios.
Different search strategies are possible by, e.g., running an ideal instance of planning-scheduling prior to the flight.}

>>>>

\vspace*{-2.6ex}
%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}  %
\label{sec:intro}       %
                        %
\IEEEPARstart{U}{se cases} involving aerial robots span broadly. They comprise diverse planning and scheduling strategies and often require high autonomy under strict energy budgets. 
One such use case is coverage path planning (CPP)~\cite{choset2001coverage,galceran2013survey}, which consists of, e.g., an aerial robot visiting every point in a given space~\cite{cabreira2019survey} while running assigned computational tasks. Here, the aerial robot might detect ground patterns and notify other ground-based actors. %with little human interaction. 
Such use cases arise in %, e.g., 
precision agriculture~\cite{hajjaj2014review} 
where 
{\color{blue}information collection prior to a harvesting operation and}
%harvesting involves ground vehicles~\cite{%qingchun2012study,
%dong2011development, de2011design%,aljanobi2010setup, 
%li2008analysis, 
%edan2000robotic
%}, information collection prior to an operation as well as 
damage prevention during the operation involve aerial robots~\cite{puri2017agriculture, daponte2019review}.
Microcontrollers and heterogeneous computing hardware~\cite{mei2005case} (i.e., with CPUs and GPUs) running power-demanding computational tasks are frequently mounted onto the robots in these and many other scenarios~\cite{william2019aerial%, peng2019evaluating,
%wang2020yolo
,alexey2021autonomous}.
%In these and many others, the robot frequently mounts microcontroller and heterogeneous computing hardware~\cite{mei2005case} (i.e., with CPUs and GPUs) running power-demanding computational tasks~\cite{william2019aerial, peng2019evaluating,wang2020yolo,alexey2021autonomous}. 
We refer to onboard computational tasks that can be scheduled with an energy impact as \emph{computations}. We are interested in the energy optimization of motion plans and computations schedules in-flight and refer to it as energy-aware \emph{planning-scheduling}. 
The energy optimization of computations schedules can be achieved by, e.g., varying the quality of service between specific bounds~\cite{ho2019qos} and frequency and voltage of the computing hardware~\cite{mei2005case,brateman2006energy,zhang2007low}. We focus on the former aspect and schedule the onboard computations altering their quality while simultaneously changing the quality of the coverage.
{\color{blue} Concretely, we alter how often the aerial robot detects ground patterns along with the distance of the lines that form the coverage.}
Fig.~\ref{fig:il-abs} illustrates the intuition: an aerial robot flies a plan with maximal coverage and schedule~(\ref{sth:i}), that is optimized during flight to respect the battery state~(\ref{sth:ii}), and altered due to, e.g., unexpected battery defects~(\ref{sth:iii}).

@@

There are numerous planning approaches applied to a variety of robots. An instance is an algorithm selecting an energy-optimized trajectory~\cite{mei2004energy} by, e.g., maximizing the operational time~\cite{wahab2015energy}. Many approaches apply to a small number of robots~\cite{kim2005energy} and focus exclusively on planning the trajectory~\cite{kim2008minimum}, despite compelling evidence of the energy influence of onboard {\color{blue}computations}~\cite{mei2005case,ondruska2015scheduled,sudhakar2020balancing,brateman2006energy}. In view of the availability of powerful heterogeneous computing hardware~\cite{rizvi2017general}, the use of onboard computations is further expected to increase in the foreseeable future~\cite{%abramov2012real,
%satria2016real,
jaramillo2019visual}. In this context, planning-scheduling energy awareness is a recent research direction% energy awareness for mobile robots are scarce
~\cite{brateman2006energy,sudhakar2020balancing,lahijanian2018resource,ondruska2015scheduled}. Early studies (2000--2010) varied hardware-dependent aspects, e.g., frequency {\color{blue}and} voltage, along with motion aspects, e.g., motor and travel velocities~\cite{mei2005case,brateman2006energy,zhang2007low,sadrpour2013mission} whereas the literature from the past decade derives energy-aware plans-schedules in broader terms. These include simultaneous considerations for planning-scheduling in perception~\cite{ondruska2015scheduled}, localization~\cite{lahijanian2018resource}, navigation~\cite{ho2019qos}, and anytime planning~\cite{sudhakar2020balancing}.
These studies are focused on ground-based robots~\cite{mei2005case,sadrpour2013mission,lahijanian2018resource,ondruska2015scheduled}, yet, aerial robots are particularly affected by energy considerations, as it would be generally required to land to recharge the battery. 
{\color{blue}In terms of aerial coverage, past work considers criteria including the completeness of the coverage and resolution~\cite{difranco2015energy}, and deals with aspects such as the quality of the cover~\cite{difranco2016coverage}, but neglects the energy expenditure of computations and favors rotary-wing aerial robots rather than aerial robots broadly.} 
Such a state of practice has prompted us to propose the planning-scheduling approach for autonomous aerial robots, combining the past body of knowledge but addressing aerial robots' peculiarities such as the atmospheric, battery, and turning radius constraints. Numerical simulations and experimental data of both static and dynamic plans and schedules show improved power savings and fault tolerance with the %aerial 
robot %s
remedying in-flight failures.

Our focus is on fixed wings, i.e., airborne robots where wings provide lift, propellers provide forward thrust, and control surfaces perform maneuvering. Here, motion and computations energies are within an order of magnitude from each other~\cite{seewald2020mechanical}. %Indeed 
{\color{blue}T}here are other classes where planning-scheduling energy awareness leads to irrelevant savings, i.e., when the motion energy contribution far outreaches the computations or vice-versa. The {\color{blue}motion outreaching computation energy} frequently happens with rotary-wing aerial robots (e.g., quadrotors or quadcopters, hexacopters, etc.){\color{blue}, the opposite occurs with} lighter-than-air aerial robots (e.g., blimps). It is a common theme {\color{blue}in} wider planning-scheduling literature, focusing on energy-efficient ground-based robots such as Pioneer~3DX~\cite{ho2019qos,mei2005case}, ARC~Q14~\cite{ondruska2015scheduled,lahijanian2018resource}, and Pack-Bot~UGV~\cite{sadrpour2013mission}.
%\begin{ctb}
%  We extend the literature on planning-schedu- ling to CPP with aerial robots, model the overall and computations energies and battery evolution, and derive a variable coverage motion for constrained systems, e.g., fixed wings.
%\end{ctb}

To guarantee energy awareness, our approach uses optimal control {\color{blue} and heuristics} where both the paths and schedules variations are trajectories, varying between given bounds (i.e., physical constraints of the robot and computing hardware, quality of service, desired quality of the coverage, etc.). Past planning-scheduling studies also employ optimization techniques~\cite{brateman2006energy,zhang2007low,ondruska2015scheduled,lahijanian2018resource}; some use a greedy approach~\cite{mei2005case,sudhakar2020balancing,sadrpour2013mission}; whereas others use reinforcement learning-based approaches~\cite{ho2019qos,ho2018towards}. {\color{blue}Hybrid approaches~\cite{ondruska2015scheduled} are also available, where the techniques are mixed.} Both the path{\color{blue}s} and schedules variations trajectories are derived for future time instants employing computations and overall energies and battery models. The energy model for the computations uses regressional analysis from our earlier study on heterogeneous computing hardware% energy modeling
~\cite{seewald2019coarse,seewald2019component}, whereas the battery uses an equivalent circuit model (ECM) from the literature~\cite{%he2011evaluation,
hinz2019comparison,mousavi2014various}. The overall model wraps these two aspects in a cohesive model that uses dynamics modeling to predict the energy behavior of future plans and schedules. In Fig.~\ref{fig:il-abs}, collected energy data ({\color{blue}top-right}) and spectrum analysis ({\color{blue}below}) of a fixed wing %aerial robot 
flying CPP motivate the overall energy model: the evolution is periodic--CPP often involves repetitive motions to cover the space~\cite{choset2001coverage,galceran2013survey}--an observation exploited in Section~\ref{sec:energy-model}.% for the computations and motion energies and battery models.

@@

\begin{figure}[t]
  \footnotesize
  \begin{minipage}[l]{0.38\columnwidth}
    \caption{Definitions~\ref{def:stage}--\hyperref[def:plan]{4} on a slice of the plan $\Gamma$. $\mathbf{p}_{\Gamma_i}$ are triggering points in which proximity happens {\color{blue}the} change of stages $\Gamma_i$. Each contains a path function $\varphi_i$ and parameters to alter the path and schedule $c_{i,1},\dots$.}
    \label{fig:traj1}
  \end{minipage}\hfill
  \begin{minipage}[c]{0.6\columnwidth}
    \centering
    \vspace*{-4ex}
    \input{\figpath/new/traj1.tikz}
  \end{minipage}
  \vspace*{-4.5ex}
\end{figure}

@@

\begin{defn}[Stage]\label{def:stage}
  Given a generic point $\mathbf{p}\in\mathbb{R}^2$ w.r.t. a reference frame $\mathcal{O}_W$ of the aerial robot flying at a given altitude $h\in\mathbb{R}_{>0}$, the $i$th \emph{stage} $\Gamma_i$ %at time instant $t$ %of a plan $\Gamma$ 
  is
  \begin{equation*}\begin{split}
    \Gamma_i:=\{{\color{blue}\varphi_i(\mathbf{p}%(t)
    ,c_i^\rho)},c_i^\sigma\mid
    \,&\forall j\in\,[\rho]_{>0},\,c_{i,j}\,\,\,\,\,\,\,\in\mathcal{C}_{i,j},\,\\
      &\forall k\in[\sigma]_{>0},\,c_{i,\rho+k}\in\mathcal{S}_{i,k}\,\},
  \end{split}\end{equation*}
  where $c_i^\rho${\color{blue}$:=\{c_{i,1},c_{i,2},\dots,c_{i,\rho}\}$} and $c_i^\sigma${\color{blue}$:=\{c_{i,\rho+1},c_{i,\rho+2},\dots,$ $c_{i,\rho+\sigma}\}$} are $\rho$ \emph{path} and $\sigma$ \emph{computation parameters}{\color{blue}, e.g., $c_i^\rho:=\{c_{i,1}\}$ is a value that changes the distance of the coverage lines and $c^\sigma_i:=\{c_{i,2}\}$ the detection rate with $\rho$ and $\sigma$ being one (see Section~\ref{sec:experimental})}. $\mathcal{C}_{i,j}:=[\underline{c}_{i,j},\overline{c}_{i,j}]\subseteq\mathbb{R}$ is the $j$th path parameter %$c_{i,j}$ 
  constraint set, %and 
  $\mathcal{S}_{i,k}:=[\underline{c}_{i,\rho+k},\overline{c}_{i,\rho+k}]\subseteq\mathbb{Z}_{\geq 0}$ %is 
  the $k$th computation parameter constraint set. {\color{blue}Indices $j,k$ serve~to~differentiate path and computation parameters constraints and indicate that each parameter can have a different constraint set.} 
\end{defn}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Energy Models}  %
\label{sec:energy-model} %
                         %
The solution to the problem requires energy models, predicting the impact of changes to path and computation parameters on the battery. %at future time instants. To this end, 
Sections~\ref{sec:mod-mot}--\hyperref[sec:mod-bat]{C} {\color{blue}thus} provide models for the overall and computations energies {\color{blue}and }%as well as 
battery evolution.

@@

{\color{blue}Matrices $A$ and $C$ are constructed such that t}he %Under favorable conditions, %the 
models in Eqs.~(\ref{eq:fourier}--\ref{eq:state-perf}) are equal
%\begin{lem}[Signal, output equality]\label{lem:eqv}Given 
when $\mathbf{u}$ is a zero vector %, matrices $A,C$ described by Eqs.~(\ref{eq:mat_A}--\ref{eq:mat_C}), 
and an initial guess $\mathbf{q}(t_0)=\mathbf{q}_0$ at {\color{blue}the} initial time instant $t_0$
  {\color{blue}\begin{equation}
  {\color{black}\mathbf{q}_0=\begin{bmatrix}a_0 & a_1/2 & b_1/2 & \cdots & a_r/2 & b_r/2\end{bmatrix}',}
  \end{equation}}
  %$h$ in Eq.~(\ref{eq:fourier}) is equal to $y$ in Eq.~(\ref{eq:state-perf}).
%\end{lem}
%\begin{proof}
%The equality of the signal and output is achieved by a proper choice of the items of matrices $A,C$ and the initial guess $\mathbf{q}_0$. We refer the reader to Appendix~\ref{app:proof-eqv} for a formal proof, where we justify the choices of the items of the matrices and of the initial guess. 
%\end{proof}
%Appendix~\ref{app:proof-eqv} contains a proof of Lem.~\ref{lem:eqv}.
i.e., $h,y$ are %both 
harmonic signals with the same frequencies{\color{blue}. For further details see the first author's Ph.D. thesis~\cite{seewaldphdthesis}}.

@@

Eq.~(\ref{eq:state-perf}) states that the output $y$ evolves in $\mathbb{R}$, %conflicting with the the findings in this section. 
yet, aerial robots usually use a battery.
We thus use instead
%\begin{defn}[Output constraint]\label{def:const}
\begin{equation}\label{eq:output-const}
  {\small\mathcal{Y}(t):=\{y\mid y\in[0,b\,Q_cV]\subseteq{\mathbb{R}_{\geq 0}}\},} 
\end{equation}
%the \emph{output constraint}, 
where $b\,Q_cV$, the maximum instantaneous energy %consumption
measured in watts, is derived from Eq{\color{blue}s}.~(\ref{eq:batdyn}--\ref{eq:batdyn2}).
%\end{defn}

@@

%The algorithm that we presented in this paper is motivated by a periodic behavior of empirical data on energy consumption (see the subfigures of Fig.~\ref{fig:il-abs}). 
Fig.~\ref{fig:il-abs} details the data of the physical flight  
%We collected these data flying Opterra, a fixed-wing UAV that we adapted for an agricultural scenario. The UAV was flying 
in standard atmospheric conditions. 
Fig{\color{blue}s}.~\ref{fig:stat}{\color{blue}--\ref{fig:dyn}} extends the flight with the computing hardware aided by a flight simulation implemented in \textsc{Matlab}\hspace{.5ex}(R). 
Upper-case roman numerals I,II indicate the plans are static (i.e., solely Algorithm~\ref{alg2}), lower-case i,ii exploit planning-scheduling as described in this letter.

@@

Fig{\color{blue}s}.~{\color{blue}\hyperref[fig:stat]{6a}--\hyperref[fig:dyn]{7a}} 
illustrate the same plan $\Gamma$ under different conditions. Flights \hyperref[fig:trajs-I-static]{I}--\hyperref[fig:trajs-dyn-i]{i} have a constant wind speed of five meters per second, a wind direction of zero degrees, and initial parameters $c_{i,1},c_{i,2}$ values of zero and ten (i.e., full $r_2$ and detection). Flights \hyperref[fig:trajs-II-static]{II}--\hyperref[fig:trajs-dyn-ii]{ii} (see added gray background for clarity) are the same but a wind direction of 90 degrees and the initial parameters values of -1000 and two (i.e., minimum $r_2$ and detection). 
{\color{blue} The initial values of path and computation parameters are chosen to represent the highest and lowest configurations in the search space in \hyperref[fig:trajs-I-static]{I}--\hyperref[fig:trajs-dyn-i]{i} and \hyperref[fig:trajs-II-static]{II}--\hyperref[fig:trajs-dyn-ii]{ii} respectively, modeling the behavior of the best- and worst-case scenarios.
Different search strategies are possible by, e.g., running an ideal instance of planning-scheduling prior to the flight.}
